Measuring causal influence with\\ back-to-back regression

### 2019-05-22 paper/meg_exps.tex
Sync
it builds

We then estimate the contribution
$diag(\hat E) \in\mathbb{D}^{d} $ of each factor. However, $H\in\mathbb{R}^{d,
q}$ is a matrix of $d$ word features by $q$ MEG channels. We approximate
the relative contribution of each feature with the sum-of-squares of the corresponding coefficients in $H$; for the $j$-th feature:
\begin{equation}
  \hat e_j = \sum_{i=0}^{q} {h_{i,j}}^2
\end{equation}
\paragraph{Backward regression} or 'decoding', is similar but predicts $X$ from $Y$:
\begin{equation} G = (Y^{T}Y+\lambda I)^{-1} Y^{T}X \end{equation}
where $\lambda$ is cross-validated as for encoding. We estimate the
contribution $diag(\hat E) \in\mathbb{D}^{d} $ of each factor in the following
way. We predict $X$ on a held-out split \textit{(train, test)}:
% Using 10-fold cross-validation, we thus assessed the ability of this ridge
% regression to predict independent and identically distributed data:
\begin{equation} \hat X_{test} = Y_{test}\cdot G_{train} \end{equation}
and assess, for each factor of X independently, the Pearson correlation
coefficient $r$ between $X_{test}$ and $\hat X_{test}$. We repeat the procedure
for 20 random splits and average the result.

\paragraph{Back-to-back regression} We adapted back-to-back regression with two
changes. First, to avoid getting a slightly positively-biased estimate of the
factors contributing to the MEG signal, we swap the Tikhonov regularization of
the first regression $G$ with a trunkated regularization. Trunkation was fitted
 by maximum likelihood estimate, as implemented in scikit-learn principal
 component analysis. Second, to minimize the variance increase induced by
 bagging, we computed the inverse regularized covariance matrices outside
 bagging:
\begin{equation}
G = (Y_^T Y+\lambda_Y I)^{-1} Y_i^T X_i
\end{equation}

>>>>

We then estimate the contribution
$diag(\hat E) \in\mathbb{D}^{d} $ of each factor. However, $H\in\mathbb{R}^{d,
q}$ is a matrix of $d$ word features by $q$ MEG channels. We approximate
the relative contribution of each feature with the sum-of-squares of the corresponding coefficients in $H$; for the $j$-th feature:
\begin{equation}
  \hat e_j = \sum_{i=0}^{q} {h_{i,j}}^2
\end{equation}
\paragraph{Backward regression} or 'decoding', is similar but predicts $X$ from $Y$:
\begin{equation} G = (Y^{T}Y+\lambda I)^{-1} Y^{T}X \end{equation}
where $\lambda$ is cross-validated as for encoding. We estimate the
contribution $diag(\hat E) \in\mathbb{D}^{d} $ of each factor in the following
way. We predict $X$ on a held-out split \textit{test}:
% Using 10-fold cross-validation, we thus assessed the ability of this ridge
% regression to predict independent and identically distributed data:
\begin{equation} \hat X_{test} = Y_{test}\cdot G_{train} \end{equation}
and assess, for each factor of X independently, the Pearson correlation
coefficient $r$ between $X_{test}$ and $\hat X_{test}$. We repeat the procedure
for 20 random splits and average the result.

\paragraph{Back-to-back regression} We adapted back-to-back regression with two
changes. First, to avoid getting a slightly positively-biased estimate of the
factors contributing to the MEG signal, we swap the Tikhonov regularization of
the first regression $G$ with a truncated regularization. Truncation was fitted
 by maximum likelihood estimate, as implemented in scikit-learn principal
 component analysis. Second, to minimize the variance increase induced by
 bagging, we computed the inverse regularized covariance matrices outside
 bagging:
\begin{equation}
  G = (Y^T Y+\lambda_Y I)^{-1} Y_{train}^T X_{train}
\end{equation}
\begin{equation}
\hat X_{test} = Y_{test} \cdot G^T
\end{equation} where $\left(train,test\right)$ are partitions of the data.
